\clearpage
\section{Introduction}
\subsection{Executive Description}

Retro nearby flight information display.

\subsection{User Stories}
\begin{flushleft}
[User Story 1 – The Long-Time Aviation Hobbyist
	As a long-time aviation hobbyist who has spent years tracking flights through phone apps, I’m tired of paying for subscriptions just to unlock basic features. 
    I want a device that gives me real-time flight information without hidden costs, while also providing a tactile, nostalgic experience that reminds me of classic aviation boards. 
    By having the Aviator on my desk, I can finally stay connected to the aviation world without feeling like I’m paying a premium for something that should be standard and accessible.]    
\end{flushleft}
\newline
\begin{flushleft}
[User Story 2 – The Casual Aviation Enthusiast
	As someone with a general interest in aviation, I don’t need a full cockpit-level tracker, but I do want something that feels engaging and easy to use. 
    Standard apps are flat, cluttered, and frankly too much for a novice like myself, but the Aviator project makes flight tracking simple, physical, and fun. 
    I can glance at the board, see arrivals and departures, and feel connected to the aviation scene effortlessly. The setup process was simply plug and play. 
    Additionally, I don’t have to pay a dime for the product. For me, it’s about accessibility and enjoying aviation in a personal,low-effort, high-impact way.]
\end{flushleft}
\\\\
\begin{flushleft}
[User Story 3 – The Purdue ECE Student
	As a Purdue ECE student, I’m drawn to the Aviator not only as a hobby project that I can tinker with, but also as a nod to Purdue’s deep aviation legacy. 
    It’s inspiring to own a piece of tech that bridges my academic interests in circuits and embedded systems with Purdue’s reputation in aerospace. 
    I want a tracker that feels hands-on, customizable, and personal—something that makes me feel part of both my field of study and Purdue’s aviation history every time I glance at it. 
    Given the nature of the project and its ability to be completed by an individual excites me, as it gives me the stepping stone I needed to start tracking flights.]
\end{flushleft}