\clearpage
\section{Design Requirements}
\subsection{Requirements}
\begin{enumerate}
      \item The device must display accurate information.
      \item The display must not interfere with
            user's well-being by, for example, displaying at
            excessive luminosity, updating rapidly
            in a distracting manner, or being
            excessively bulky.
      \item The device must not infringe on any person's
            reasonable expectation of privacy.
      \item The device must
            be language-agnostic wherever possible.
      \item The device must be responsive and intuitive.
      \item The device must have robust error handling and recovery.
      \item The physical device should be
            easily replicated with widely available
            parts.
      \item The code for the device must
            be open-source and well-documented.
      \item The device should be as durable and
            environmentally friendly as possible so as
            not to contribute to e-waste.
      \item The device must not contribute to noise
            or visual pollution of any space.
      \item The device must be energy-efficient.
      \item The device must minimize
            construction and recurring costs.
      \item The device must not infringe on
            right to repair.
      \item The device must mount and dismount without
            damage to vertical surfaces.
\end{enumerate}

\clearpage

\subsection{Factors Influencing Requirements}
\subsubsection{Public Health, Safety, and Welfare}
\begin{enumerate}
      \item User well-being
      \item Privacy
\end{enumerate}

\subsubsection{Cultural Factors}
\begin{enumerate}
      \item Language differences
      \item Ease of use
\end{enumerate}

\subsubsection{Social Factors}
\begin{enumerate}
      \item Ease of replication
      \item Open-source and documentation
\end{enumerate}

\subsubsection{Environmental Factors}
\begin{enumerate}
      \item Environmental friendliness and e-waste
      \item Noise and visual pollution
      \item Energy efficiency
\end{enumerate}

\subsubsection{Economic Factors}
\begin{enumerate}
      \item Cost
      \item Repairability
\end{enumerate}